### 2020-12-03 fe_px_paper/Response_to_Reviewers.tex

% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\usepackage[american]{babel}

\usepackage [autostyle, english = american]{csquotes}
\usepackage[version=3]{mhchem} 
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage[ampersand]{easylist}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{amsmath}

\newfloat{figure}{htbp}{figs}

% \newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}
\newcommand{\colornote}[1]{\textcolor{red}{#1}}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\pp}[1]{\left( #1\right)}

\begin{document}

\signature{Andrew S. Voyles}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Dr. Jose Benlliure \\
Editor \\
European Physical Journal A}

\begin{flushleft}
{\large\bf Andrew S. Voyles, Ph.D.}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
% \hfill The University of California, Berkeley \\
\hfill Lawrence Berkeley National Laboratory \\
\hfill Building 088-163D  |  M/S 88R0192, Berkeley, CA  94720-1730 \\
% \hfill (presently) +47 486 43 444 \\ 
\hfill  +1 (850) 281-0217 (mobile) or +1 (510) 486-7310 (office) 
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Dr. Benlliure,}

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in European Physical Journal A.  Please find my responses detailed in \colornote{red text.}

  \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.  We would especially like to thank the referees for their thorough reading and critique, which has made it a better paper. Their comments were very constructive and pointed out some valuable improvements.

  Please find the feedback following here, and our revised manuscript attached.

  Sincerely yours,\\ \\ \\ \\ Andrew S. Voyles

% \closing{Sincerely yours,}

  \vfill

 \pagebreak

 Referee \#1:

Authors have measured cross sections of the natFe(p,x), natCu(p,x) and natTi(p,x) reactions and done
model calculations using several codes with default parameters. No meaning of model calculations using
default parameter, author should adjust input parameter to fit experimental data.
It seems the paper related to measure cross sections for production of medical isotopes via proton
induced reactions on natFe, which play role to optimize production route; impurities, optimum energy
window, yield, etc. In this paper the above objects are not clearly presented. I would like to suggest to
calculate integral yields and discuss in details.
No meaning of the natCu(p,x) and natTi(p,x) reactions cross section measurements except monitor
reactions. Excitation functions of the monitor reactions induced on Cu and Ti should be determined and
compared with the IAEA recommended curve, which confirms experimental techniques and beam
parameters. Therefore, other reactions from Cu and Ti monitor should be omitted from the paper.

%   \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

Few more comments:

1. P-2, line-15, ‘...........our measured data to probe the role of angular momentum...’.It should
clear and details in discussion.

2. Sample size 2.5 cm x2.5 cm is too large. What is the benefit of such sample size?

3. The notifications ’25 MeV stack’ and ’55 MeV stack’ are not correct.

4. Fig.1 is not special. Setup of 88-inch cyclotron is well characterized. The Fig. 1 should be
omitted.

5. In Fig.2, peak should be identified by energy and nuclide, not by symbol.

6. In Fig.3, why the trend of one stack is different from other.

7. EoB should be replaced by EOB.

8. What is the meaning of value in bracket in Tables.

9. P-8, line 44, ‘The natFe, natCu and natTi(p,x)......’ is not proper writing.

10. Both the numerical values for all investigated reactions should be given in Table and discussed in
details. But author did not discuss details for the reactions in Appendix.

Furthermore, the English and Writing as well as presentation is very poor. I can not recommend for
publication in the present form. It should be revised.

 \colornote{We thank the reviewer for their thoughtful comments....\\\\ ???????}

\pagebreak

 Referee \#2:

The paper \enquote{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV} describes three (six) comprehensive measurement campaigns obtaining data for the production of radioactive nuclides produced by the interaction of protons with natural iron, copper and titanium. The purpose is the determination of accurate excitation curves in support of investigations into alternative or optimized routes for the production of medical radionuclides. The authors use state of the art methods that are described in some detail in this paper and in some further detail in earlier papers involving some of the authors. Two stacks were irradiated for each material at two different energies 55 MeV and 25 MeV. Proton energy is further varied by energy loss straggling in the stack allowing up to 14 different energies from 4 to 53 MeV. The issues with this method concern the proper estimates of average proton energy per foil and the actual flux spectrum. The method is corrected/calibrated using monitor foils with well-determined cross sections but different energy dependence. The spread in results for these monitor foils has to be minimized by the estimates of proton energy and proton fluence spectra. Two methods are used. The first involves the use of FLUKA, a well-known simulation code with a long record of use in a variety of problems. The other method is not clearly described. The uncertain foil thicknesses (Al degraders, and kapton for 25 MeV) were adjusted to minimize the variation in fluence estimates from the one but last stack of monitor foils. The success of the method is demonstrated in Figure 3.
Provided the comments below are clarified, a large number of important new results are obtained. For reactions studied earlier, the accuracy is better than previous single measurements and the agreement with earlier results is good. There are a large number of reaction channels with first data (9 excitation curves, 7 for cross sections and 2 for branching ratios). By itself, these excellent new data obtained by careful experimental methods warrant accepting this publication, after taking care of the modifications suggested below. The paper further offers a clear warning against unchecked use of model calculations, even if performed with the latest developments in nuclear modelling codes. For work requiring even modest accuracy (say 20\%), these codes cannot be used to satisfaction. This warning may be more clearly highlighted in the conclusions of this paper.

\colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

Improve the description of the fitting method for minimizing the variance in the experimental fluence. The method is not clear now. Does this use AZ stopping powers and some semi-analytical approach? Expressions used?

\colornote{We thank you for raising this point, and apologize for this being unclear - we attempted to avoid duplication of much of the extensive discussion for this technique, as detailed in our previous work. We have now expanded upon this discussion in section 2.4, to make our methods more clear.  \\\\In short, FLUKA transport simulations were performed multiple times, globally perturbing the effective areal density (as a correction for the FLUKA stopping power model) of the aluminum degraders. Since each energy compartment, containing a Ti , Fe, and  Cu foil, within our stack has 4 independent monitor reactions, the perturbation in degrader density seeks to find which iteration minimizes the standard deviation of these 4 measurements, as the energy spectra from this iteration will best reproduce the IAEA-recommended monitor standard data. Since the thresholds and peaks of these different monitor reactions occur at different energies, a larger variance will be seen as the energy assignments are further away from those that reproduce the IAEA monitor data.  This is shown in a simple example in the attached figure.  So, no expressions are used here - simply finding the iteration which minimizes the standard deviation of the monitor reaction fluences.}

\begin{figure}
 \centering
 \includegraphics[width=0.7\textwidth]{./minimize_fluka_55.pdf}
 % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
%  \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment. Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks. }
%  \label{fig:gspec_femn}
\end{figure}

\colornote{Additionally, I removed the language in this section comparing the minimization results between AZ calculations and FLUKA, as well as Figure 4, which attempted to visually convey this, but I fear caused more confusion than it helped.  Most of the information needed is found in Figure 3B already, so this also helps avoid unnecessary duplication. Since we do not use the linear fit, AZ fluences estimates, or the FLUKA fluence model for any of our actual analysis,  having these in here might have partly led to the confusion.  Of all of this, only the FLUKA energy spectra (which lead to fluences when normalizing to IAEA monitor data) is actually used in our analysis, so I cut the rest to avoid any confusion in the final manuscript.  I hope that helps clarify things for you!}

The 55 MeV and 25 MeV irradiations have overlap: some energies are covered by both irradiations. This can be used to check the consistency of the methods used. However, the results do not clarify which results were obtained with which irradiation so that the reader cannot assert this consistency. Please, clearly specify which data were obtained from each of the two irradiations and show how consistent these are. A new plot or table may be necessary.

\colornote{We thank you for this very thoughtful suggestion. Running two overlapping stacks to build confidence through consistency was our goal for this, but the assignment of each foil to a stack is not clear, as you point out.  Tables 1--4, containing all of the measured cross section and ratio data, have all had a new row added, clearly designating the foil corresponding to each proton energy.}

The discussion speaks about the natural iron results in some detail, but almost nothing is said about the irradiations of natural copper and titanium. Please expand the discussion to obtain a fair description of all results.

I strongly suggest creating three figures in the main text, one for each of the irradiate materials (i.e. take these out of the annex). They should support the discussion about the results. In principle, a discussion should follow the pattern: short statements about the comparison to earlier work by channel, short statements about the agreement with models by channel; overall agreement to earlier data and to particular models. Of course, a grouped approach can be taken (several channels of a given nature). Separate messages about the data and their agreement with model estimates from the potential use of the results. Usefulness of the results should be either in the introduction or in an outlook at the end. There is also where implications should be highlighted (outlook at the end of the paper).

Highlight clearly in the conclusions that model estimates are inadequate for even modest accuracy targets (like 20\%).

\colornote{We thank your for making this important point particularly clear. This point is a vital takeaway from this work, which was not made explicit enough, but has now been more directly addressed in the conclusions.}

If each activation foil is covered on both sides with kapton adhesive then this could be more clearly explained by either a drawing or the explicit mention of this in the tables describing the stacks.Please make this very explicit and mention clearly the best estimates for composition and thickness of these foils.

\colornote{We thank your for this point.  The language in section 2.1 has been updated to reflect this, and a short statement to this effect has been added to the caption of Table 6.}

% \encl{}  				% Enclosures

\end{letter}

\end{document}

### 2020-12-03 fe_px_paper/fe_body_text.tex
Preparation for 2nd round PU review

We constructed a pair of target stacks 
% were constructed 
for this work,
% , due to the large energy range desired to be spanned.
one stack covering the 55--20\,MeV range and the other  25--0\,MeV.
% , in order to 
This minimized the systematic uncertainties associated with significant degradation of beam energy, and
% In addition, the complementary  energy  of the  stacks helps build confidence  through 
included multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
% to build confidence in the results. 
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils 
% of each metal 
were cut down to 2.5$\times$2.5\,cm squares and spatially characterized 
% --- for each foil, length and width measurements were taken 
at four different locations using a digital caliper and micrometer (Mitutoyo America Corp.).
% , thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and 
Four mass measurements were performed using an analytical balance 
% after cleaning the foils with isopropyl alcohol.
% Using these length, width, and mass readings, the 
in order to determine their areal density. 
% and its uncertainty 
% (in mg/cm$^2$).
% for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were  sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape 
% --- each piece of tape consists 
consisting of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Plates of 6061 aluminum alloy  served as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy and mounts on the end of an electrically-isolated beamline.
The specifications of both target stacks 
% designs for this work are presented 
are in \autoref{tab:fe_stack_table} of 
% Appendix 
\ref{sec:fe_stack_design}.

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.75\textwidth]{./figures/sample_gspec_fe.pdf}
 % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
 \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment. Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks. }
 \label{fig:gspec_femn}
\end{figure*}

@@

% To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
% used in this work 
should all be consistent at each 
% energy 
position.
% Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, 
% Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
% % stack design, namely, the
% areal densities of the stack components. 
This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties.
% in stack areal densities.

When performing  a variance minimization, it is important to apply this variation of effective areal density  to the stack components which  have the most significant impact on beam energy loss.
% degradation, as any systematic error in the areal densities used for these components will cause a disagreement in the observed fluences.
% For the 55\,MeV stack
Therefore, the aluminum degraders are used for variance minimization for the 55\,MeV stack, as they make up more than 80\% of the areal density of the stack.
% , and thus play the largest role in beam degradation.
For the 25\,MeV stack, the Kapton tape was chosen for variance minimization, as the foil packets themselves are responsible for the majority of beam degradation.
While it only makes up approximately 20\% of the low-energy stack's areal density, the Kapton surrounding each foil packet has a greater areal density than the foil itself.
In addition, it is far easier to directly characterize the areal density of the metallic foils than it is for the Kapton, resulting in only an approximate value for the latter.
% While it might seem obvious, t
The contributions to the slowing of the beam due to the adhesive have often been neglected in much work performed to date. 
This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but 
% the stopping power of the Kapton 
becomes increasingly important for proton energies below 
% approximately 
25\,MeV, causing as much as an additional loss of 8\,MeV  by the time it reaches the end of the stack.
% by the rear of this stack.
% , making the precise areal density a source of significant uncertainty.

In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  was varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Ti-07, Cu-07).
For the 25\,MeV stack, the areal density reached in the minimization of the 55\,MeV stack was used for  the E-09 and H-01 aluminum degraders
% was taken from that reached in the minimization of the 55\,MeV stack.
% Using this value, 
and the areal density of each of the  Kapton tape  layers  was 
% likewise 
varied 
% uniformly   
by 
% a factor of up to 
$\pm$25\%, 
% of nominal values
to find the effective density which minimized variance in the measured proton fluence at the next-to-lowest energy position (Ti-19, Cu-19).
These 
% lowest energy 
positions were chosen as  minimization candidates as they are the most sensitive to systematic uncertainties in stack design.
% , due to the compounded effect of proton stopping powers.
In the 25\,MeV stack, activity was not seen in gamma spectrometry for the lowest-energy (Cu-20) monitor foil, implying that the beam was stopped at some point in between Ti-20 and Cu-20.
This observation 
% is conclusive proof 
indicates that  the true areal densities of the stack components differ from nominally measured values (primarily for the difficult-to-characterize Kapton tape), as transport calculations using nominal areal densities predict that the beam should exit the stack 
% (at the SS-6 profile monitor) 
with an energy of approximately 7\,MeV.
As a result, this position was not used for minimization, with the Ti-19 and Cu-19 position being the lowest-energy reliable monitor foils in the stack.
% % Remove these next two liens for the journal version
% % 
% With the exception of two foils (Cu-20 and Ti-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
% % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
% This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Fe-14 and Ti-20.
% 
% Re-introduce the rest of this paragraph for the journal version
% 
% 
The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average 22.71\,MeV protons entering the last energy position of the 55\,MeV stack.
This is approximately 2\,MeV lower than the 
% nominal 
FLUKA simulations, and approximately 2\,MeV lower than 
% nominal 
A\&Z calculations, both of which used the nominal 2.80\,g/cm$^3$ measured density of the  aluminum degraders.
This energy corresponds to an aluminum areal density  4.43\% greater than 
% nominal 
measurements and 
% serves as a lump correction 
corrects for other minor systematic uncertainties in stack design.
% , including stack areal densities and incident beam energy.
Similarly, for the 25\,MeV stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations, and approximately 5\,MeV lower than nominal A\&Z calculations.
This energy corresponds to a Kapton tape areal density of 5.69\% greater than nominal measurements, which is completely reasonable given the lack of areal density data from the manufacturer.
The impact of this variance minimization for improving disagreement in proton fluence is  clearly  seen in   \autoref{fig:fe_variance_mins}.

@@

        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fe_after_minimization}
   \hspace{-5pt}}%
    \caption{Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack). A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.  Open data points represent the 25\,MeV stack, and closed data points represent the 55\,MeV stack.} 
     \label{fig:fe_variance_mins}
\end{figure*}

>>>>

We constructed a pair of target stacks 
% were constructed 
for this work,
% , due to the large energy range desired to be spanned.
one stack covering the 55--20\,MeV range and the other  25--0\,MeV.
% , in order to 
This minimized the systematic uncertainties associated with significant degradation of beam energy, and
% In addition, the complementary  energy  of the  stacks helps build confidence  through 
included multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
% to build confidence in the results. 
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils 
% of each metal 
were cut down to 2.5$\times$2.5\,cm squares and spatially characterized 
% --- for each foil, length and width measurements were taken 
at four different locations using a digital caliper and micrometer (Mitutoyo America Corp.).
% , thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and 
Four mass measurements were performed using an analytical balance 
% after cleaning the foils with isopropyl alcohol.
% Using these length, width, and mass readings, the 
in order to determine their areal density. 
% and its uncertainty 
% (in mg/cm$^2$).
% for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were  sealed into \enquote{packets} between two pieces of  3M 5413-Series Kapton polyimide film tape,  
each piece of tape 
consisting of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Plates of 6061 aluminum alloy  served as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy and mounts on the end of an electrically-isolated beamline.
The specifications of both target stacks 
% designs for this work are presented 
are in \autoref{tab:fe_stack_table} of 
% Appendix 
\ref{sec:fe_stack_design}.

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.75\textwidth]{./figures/sample_gspec_fe.pdf}
 % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
 \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment. Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Mn} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks. }
 \label{fig:gspec_femn}
\end{figure*}

@@

% To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used here to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
% used in this work 
should all be consistent at each 
% energy 
position.
% Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, 
% Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
% % stack design, namely, the
% areal densities of the stack components. 
This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties.
% in stack areal densities.
As in  our prior work, variance minimization treats the effective density of a sensitive set of stack components (such as degraders) as a free parameter in proton transport calculations, to optimize agreement with the IAEA-recommended charged particle monitor standards.
Across multiple iterations of these simulations, this parameter is uniformly varied to find the energy spectra for each foil which minimizes the standard deviation  of the multiple measurements of proton fluence in a stack compartment.
The lowest energy position of a stack is often chosen for this, as it is the most sensitive to perturbations of the transport calculations.
It is important to note that this technique does not imply that the measured density of the stack components is incorrect --- rather, it is used as a surrogate to correct for poorly-characterized stopping power and other systematic uncertainties.

When performing  a variance minimization, it is important to apply this variation of effective areal density  to the stack components which  have the most significant impact on beam energy loss.
% degradation, as any systematic error in the areal densities used for these components will cause a disagreement in the observed fluences.
% For the 55\,MeV stack
Therefore, the aluminum degraders are used for variance minimization for the 55\,MeV stack, as they make up more than 80\% of the areal density of the stack.
% , and thus play the largest role in beam degradation.
For the 25\,MeV stack, the Kapton tape was chosen for variance minimization, as the foil packets themselves are responsible for the majority of beam degradation.
While it only makes up approximately 20\% of the low-energy stack's areal density, the Kapton surrounding each foil packet has a greater areal density than the foil itself.
In addition, it is far easier to directly characterize the areal density of the metallic foils than it is for the Kapton, resulting in only an approximate value for the latter.
% While it might seem obvious, t
The contributions to the slowing of the beam due to the tape's adhesive have often been neglected in much work performed to date. 
This is of relatively minor consequence for higher-energy irradiations (especially relative to any beam degraders), but 
% the stopping power of the Kapton 
becomes increasingly important for proton energies below 
% approximately 
25\,MeV, causing as much as an additional loss of 8\,MeV  by the time it reaches the end of the stack.
% by the rear of this stack.
% , making the precise areal density a source of significant uncertainty.

In performing the  minimization, the areal density of each of the  aluminum degraders (for the 55\,MeV stack)  was varied uniformly in FLUKA simulations  by a factor of up to $\pm$25\% of measured
% nominal 
values, to find the effective density which minimized variance in the measured proton fluence for the four monitor reactions at the lowest energy position (Ti-07, Cu-07).
For the 25\,MeV stack, the areal density reached in the minimization of the 55\,MeV stack was used for  the E-09 and H-01 aluminum degraders
% was taken from that reached in the minimization of the 55\,MeV stack.
% Using this value, 
and the areal density of each of the  Kapton tape  layers (both adhesive and backing)  was 
% likewise 
varied 
% uniformly   
by 
% a factor of up to 
$\pm$25\%, 
% of nominal values
to find the effective density which minimized variance in the measured proton fluence for the two monitor reactions at the next-to-lowest energy position (Ti-19, Cu-19).
These 
% lowest energy 
positions were chosen as  minimization candidates as they are the most sensitive to systematic uncertainties in stack design.
% , due to the compounded effect of proton stopping powers.
In the 25\,MeV stack, activity was not seen in gamma spectrometry for the lowest-energy (Cu-20) monitor foil, implying that the beam was stopped at some point in between Ti-20 and Cu-20.
This observation 
% is conclusive proof 
indicates that  the stopping power characterization
% true areal densities of
for the stack components 
% differs from nominally measured values 
(primarily for the difficult-to-characterize Kapton tape) is significantly underestimated, as transport calculations using nominal areal densities predict that the beam should exit the stack 
% (at the SS-6 profile monitor) 
with an energy of approximately 7\,MeV.
As a result, this position was not used for minimization, with the Ti-19 and Cu-19 position being the lowest-energy reliable monitor foils in the stack.
% % Remove these next two liens for the journal version
% % 
% With the exception of two foils (Cu-20 and Ti-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
% % \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
% This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Fe-14 and Ti-20.
% 
% Re-introduce the rest of this paragraph for the journal version
% 
%

The results of the minimization technique indicate a clear minimum in proton fluence variance for flux-weighted average 22.71\,MeV protons entering the last energy position of the 55\,MeV stack.
This is approximately 2\,MeV lower than the 
nominal 
FLUKA simulations,
% , and approximately 2\,MeV lower than 
% nominal 
% A\&Z calculations, both of 
which used the 
% nominal 
2.68\,g/cm$^3$ measured density of the  aluminum degraders.
This energy corresponds to an aluminum areal density  4.43\% greater than 
% nominal 
measurements and 
% serves as a lump correction 
corrects for stopping power characterization and other minor systematic uncertainties in stack design.
% , including stack areal densities and incident beam energy.
Similarly, for the 25\,MeV stack, variance minimization converges on  flux-weighted average 9.23\,MeV protons entering the Fe-13/Ti-19/Cu-19 energy position, which is approximately 4\,MeV lower than the nominal FLUKA simulations.
% , and approximately 5\,MeV lower than nominal A\&Z calculations.
This energy corresponds to a Kapton tape areal density of 5.69\% greater than nominal measurements, which is completely reasonable given the lack of areal density data from the manufacturer.
The impact of this variance minimization for improving disagreement in proton fluence is  clearly  seen in   \autoref{fig:fe_variance_mins}.

@@

        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fe_after_minimization}
   \hspace{-5pt}}%
    \caption{Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack). A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.  Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack.} 
     \label{fig:fe_variance_mins}
\end{figure*}

% Re-introduce this paragraph for the journal version
% 
% An enhanced version of the final \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reaction fluences is shown in \autoref{fig:fe_fluence_plot}.
% Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
The correlated uncertainty-weighted mean  for the two \ce{^{nat}Cu}(p,x) and two \ce{^{nat}Ti}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Cu and Ti foils, respectively, and the correlated uncertainty-weighted mean  for all four monitor channels was used to determine the final fluence assignments for the Fe foils.
This correlated uncertainty-weighted mean was calculated as:
\begin{equation} \label{eq:weighted_average_beamcurrent}
    \langle I \rangle  = \frac{ \sum_{i,j} I_j  \left( \mathbf{V}^{-1}_{ij}  \right) }{\sum_{i,j}  \left( \mathbf{V}^{-1}_{ij}  \right)} 
\end{equation}
Uncertainty in each final proton fluence  is  calculated by error propagation of the individual monitor channel fluence values  at each energy position:
\begin{equation}
    \label{eq:corrWeight}
    \delta_{\langle I \rangle} = \sqrt{\frac{ 1}{\sum_{i,j}  \left( \mathbf{V}^{-1}_{ij}  \right)}} 
\end{equation}
Each element $ij$ of the covariance matrix is calculated using the robust
sandwich estimator  \cite{huber1967behavior}:
\begin{equation}
    \label{eq:Vij}
    \mathbf{V}_{ij} = \mathrm{Cov}[I_i, I_j] = \sum_{\beta} \frac{\partial I}{\partial \beta_i} \delta_{\beta_i} \mathrm{Corr}[\beta_i, \beta_j] \delta_{\beta_j} \frac{\partial I}{\partial \beta_j}
\end{equation}
where $i,j$ are the monitor reactions in a given compartment, and $\beta \in [A_0$, $\rho \Delta r$, $\lambda$, $\Delta t_{irr}$, $\int \sigma(E) \frac{d\phi}{dE}dE$]. 
% $\Sigma_{\beta_{ij}}$ is the correlation matrix for each $\beta$. 
$A_0$ is assumed to be 30\% correlated for all reactions, $\rho \Delta r$ is assumed to be 100\% correlated for reactions from the same monitor foil, $\lambda$ is assumed to be uncorrelated, $\Delta t_{irr}$ is assumed to be 100\% correlated, and $\int \sigma(E) \frac{d\phi}{dE}dE$ is assumed to be 30\% correlated for reactions from the same monitor foil.
